Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-04 paper/main.tex
some ideas for discussion scaffold

% MIH the discussion should primarily be anchored on the points the introduction concludes with. From my POV there is no need (and likely no space) to discuss results by stimulus type. Issue like different impact of attentional focus etc can be brought up in the joint paragraph that discussed how such a factor could have differentially impacted the results -- and if that would matter.
\section{Discussion}

\subsection{AO Discussion}
% Hanke et al. (2014): Compared to an audio-visual movie, this is a stimulus that leaves a much larger margin for inter-individual differences in imagining scenery, as well as actors' character and personality traits, while still preserving the time-locked presentation of information to a listener. At the same time, an auditory stimulus limits the effect of an attentional focus on the selection of a subset of simultaneously occurring auditory events, in contrast to the selection of different parts of the visual field.
% mental imagery hypthesis (s. O'Craven \& Kanwisher, 2000)
% Lerner (2011), Honey (2012), Silbert (2014) finden keine ISC in PPA? vgl. DataPaper bzgl. Hörbuch??
% setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter"
% Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv
% object und (room)geo ist vermischt
% Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.

% From Poster:
% 1. PPA shows increased activation during non-visual, complex auditory stimulation that provides incidental spatial information.
% 2. only minor temporal correlation of regressors of the audio drama & movie that were not designed for experimental research.
% 3. but still, alternative contrasts show significant clusters in auditory cortices.
% 4. inter-individual differences: for two subjects, an alternative audio-contrast shows bilaterally significant clusters whereas the primary contrast shows no significant clusters.
% 5. audio drama shows bilaterally increased activation in subject 4 in which the visual localizer shows an unilateral cluster.
% 6. nevertheless, a  complex auditory stimulus might allow individual localization of a functionally defined brain region.
% 7. results of other studies suggest7 the PPA does not exclusively process the ``spatial layout''" but ``contextual associations''.
% 8. an audio drama might be suitable as ecologically more valid ``localizer'' for a variety of brain functions.

% Unterschiedliche Qualität der Kontrast
% Warum wurde Kontrast 1 als Kontrast 1 gewählt; se\_new se\_old sind recht
% vague in der Beschreibung der Szene verglichen mit Bild; Anzahl der Events
% ergibt auch noch Sinn;

@@

\section*{General Discussion}
% Data-driven vs. Analysis-Driven
% "Abfall" einer Film-Messung
% how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
% feasibility of (multi-dimensional) localizer development with naturalistic stimuli
% Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
% CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
% was sind für Film und Audiobook die Confounds?
% Occipital Place Area (Nakamura, 2000), RSC
% Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs. Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated \citep{haeusler2016annotation, labs2015portrayed}.
\todo[inline]{why naturalistic stimuli are so cool: sinkusare2019,
    eickhoff2020}
\todo[inline]{model-driven vs. data-driven analyses}
% Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions. This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
% aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].

>>>>

\section{Discussion}

\todo[inline]{MIH: discussion should primarily be anchored on the points the
    introduction concludes with. From my POV there is no need (and likely no
    space) to discuss results by stimulus type. Issue like different impact of
    attentional focus etc can be brought up in the joint paragraph that
    discussed how such a factor could have differentially impacted the results
    and if that would matter.}

\paragraph{From Poster}: 1. PPA shows increased activation during non-visual,
complex auditory stimulation that provides incidental spatial information.

2. only minor temporal correlation of regressors of the audio drama \& movie that were not designed for experimental research.

3. but still, alternative contrasts show significant clusters in auditory
cortices.

4. inter-individual differences: for two subjects, an alternative audio-contrast
shows bilaterally significant clusters whereas the primary contrast shows no
significant clusters.

5. audio drama shows bilaterally increased activation in subject 4 in which the
visual localizer shows an unilateral cluster.

6. nevertheless, a  complex auditory stimulus might allow individual
localization of a functionally defined brain region.

7. results of other studies suggest7 the PPA does not exclusively process the
``spatial layout''" but ``contextual associations''.

8. an audio drama might be suitable as ecologically more valid ``localizer'' for
a variety of brain functions.

\subsection{AO Discussion}

Hanke et al. (2014): Compared to an audio-visual movie, this is a stimulus that
leaves a much larger margin for inter-individual differences in imagining
scenery, as well as actors' character and personality traits, while still
preserving the time-locked presentation of information to a listener. At the
same time, an auditory stimulus limits the effect of an attentional focus on the
selection of a subset of simultaneously occurring auditory events, in contrast
to the selection of different parts of the visual field.

aminoff2013: jedoch zu non-spatial stuff: Although the PHC is commonly thought
of as responding to visual stimuli, it has also been found to elicit activity
for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].

Unterschiedliche Qualität der Kontrast: Warum wurde Kontrast 1 als Kontrast 1
gewählt; se\_new se\_old sind recht vague in der Beschreibung der Szene
verglichen mit Bild; Anzahl der Events ergibt auch noch Sinn

setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett",
"Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
dem Wohnwagen ihrer Großmutter" Soundscape macht es häufiger bereits vorher
klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv object
und (room)geo ist vermischt Retrospelinal Cortex ist in Probabilistic maps
krasser als PPA.

Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
Hörbuch??

@@

\section*{General Discussion}

\subsection{Data-driven vs. Analysis-Driven}
"Abfall" einer Film-Messung

\subsection{naturalistic vs. dedicated}
how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:

\subsection{parietal and RSC activations}
Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit

\subsection{model-driven vs. data-driven analyses}
Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions. This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.

\subsection{confounds in AO and AV}

\subsection{multi-dimensional localizer???}
feasibility of (multi-dimensional) localizer development with naturalistic
stimuli.

Natural stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer an easy to implement,
(continuous,) complex, immersive, task-free paradigm that more closely resembles
our natural dynamic environment than traditional experimental designs.

why naturalistic stimuli are so cool: sonkusare2019, eickhoff2020, hamilton
